\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2020-12-24 manuscript.Rnw
Update given that 'intercept' column is now named '(Intercept)'

Survival curves for both PFS and OS are predicted using the \code{PsmCurves} class, which is setup using the input data and the parameters of the Weibull model. However, since we manually created the parameter object---meaning that the model terms were not generated using a formula interface---the input data must contain each term contained in the parameter object. We must consequently create a column of ones for the ``intercept``.

<<psm_survmods>>=
survmods_data[, intercept := 1]
survmods <- create_PsmCurves(survmods_params, 
                             input_data = survmods_data)
@

>>>>

Survival curves for both PFS and OS are predicted using the \code{PsmCurves} class, which is setup using the input data and the parameters of the Weibull model. However, since we manually created the parameter object---meaning that the model terms were not generated using a formula interface---the input data must contain each term contained in the parameter object. We must consequently create a column of ones for the intercept.

<<psm_survmods>>=
survmods_data[, ("(Intercept)") := 1]
survmods <- create_PsmCurves(survmods_params, 
                             input_data = survmods_data)
@
